%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=1in,right=0.75in,bottom=0.75in]{geometry} % Document margins

\name{Sultan Aitzhan} % Your name
\address{a.sultan@u.yale-nus.edu.sg~$\mid$~10 College Avenue West, Singapore~$\mid$~+65 8227 5594, +7 707 1051544} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Yale-NUS College} \hfill { July 2016 - May 2020 (expected)} \\ 
B.S. in Mathematical, Computational, \& Statistical Sciences. \\

{\bf Kazakh Turkish High School} \hfill { September 2011 - May 2016} \\ 
Received five distinctions for National Testing Exam. \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}

\begin{rSubsection}{Unified Transform Method for Linear Evolution Equations }{February 2019 - Present}{Supervisor: Prof. David Andrew Smith}{Yale-NUS College}
\item Conducted a study of Unified Transform Method (UTM) used to solve linear evolution equations on a finite interval for two-point boundary problems, and wrote up detailed notes explaining the use of the method. Analysed the implementation of UTM in programming language Julia by Linfan Xiao.
\item Constructed an algorithmic procedure to find an adjoint of an ordinary differential operator with multipoint homogeneous conditions. Provided the necessary theoretical framework in the form of definitions, theorems, and proofs, and successfully implemented the procedure as an algorithm in programming language Julia. Presented my results at Yale-NUS Summer Research Symposium 2019.
\item Received over SGD \$3000 to support the project from Yale-NUS College through the J Y Pillay Global-Asia Programme. 
\end{rSubsection}

\begin{rSubsection}{Sturm-Liouville Theory and Its History}{August 2018 - December 2018}{Supervisor: Prof. Chua Seng Kee}{National University of Singapore}
\item Conducted a basic study of Sturm-Liouville theory and its history as a part of Undergraduate Research Opportunity Programme in Science (UROPS) at NUS.
\item Learned about regular Sturm-Liouville problems, a qualitative theory of differential equations, and the history behind the emergence of the Sturm-Liouville Theory, and its progress in 19th and 20th centuries.
\item Presented results to the Department of Mathematics at NUS, and drafted a report documenting my findings. 
\end{rSubsection}

\begin{rSubsection}{Independent Reading Project in Number Theory}{May 2018 - August 2018}{Supervisor: Prof. Francesca Spagnuolo}{Yale-NUS College}
\item Read more than 20 mathematical papers related to four problems in number theory: gaps between prime numbers, linear equations in primes, the modularity theorem, and the Catalan's conjecture.
\item Analysed the theory and implementation of the Hardy-Littlewood Circle Method in various problems of number theory.
\item Documented my findings in the form of weekly reports, and drafted an exposition for every work read.
\end{rSubsection}

\end{rSection}

%------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Yale-NUS Admissions \& Financial Aid}{August 2017 - Present}{Student Associate, Tours \& Outreach}
\item Gave campus tours and spoke to prospective students, their families, and high school counsellors at various admission events such as college visits by junior colleges, weekly campus tours, and Open Days. 
\item
\item Regularly covered the office's reception desk at lunch hours. 
\item Engaged in conceptualisation and execution of Admissions events such as organising of Experience Yale-NUS Weekend and NUS Open Day, and representing Yale-NUS College at various school fairs.
\end{rSubsection}

\begin{rSubsection}{Yale-NUS Centre for Teaching and Learning}{August 2018 - Present}{Peer Tutor}
\item A peer tutor for YSC2209: Proof, YSC2230: Linear Algebra, YSC3206: Real Analysis, and YSC3227: Modern Algebra. Tutor around 3-4 students from all years per week, both individually and in groups.
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Information}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Python, R, Julia \\
Languages & English (fluent), Kazakh (native), Russian (native), Turkish (fluent)
\end{tabular}

\end{rSection}


\end{document}
